Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-04 writeup/gz_hubble_data.tex
Added example images to paper

@@

\begin{figure*}
\includegraphics[width=84mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
\end{figure*}

>>>>

We also expect to see changes in the apparent morphology of galaxies due to band shifting and surface brightness effects (e.g. see Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift). So we need to measure this.

\begin{figure}
\includegraphics[width=60mm]{example_ferengi2.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshirting.  \label{exampleFERENGI}}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
\end{figure*}
